---
title: "Lab Report Knapsack"
name: "lab_report_knapsack"
author: "Simon Jönsson, Fanny Karelius"
date: "`r Sys.Date()`"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{Lab Report Knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
```{r setup, include=FALSE}
library(lab6)
library(parallel)
devtools::install_github("hadley/lineprof")
library(lineprof)
set.seed(42)
m <- 2000
knapsack_objects <-
  data.frame(w = sample(1:4000, size = m, replace = TRUE),
             v = runif(n = m, 0, 10000))
```

## Introduction

In this lab we implement different solutions for the **0/1-knapsack**- and **unbounded knapsack** problem. We have implemented both a parallel and non-parallel brute force solution, a dynamic programming solution and a solution using the greedy heuristic. We have documented the runtimes and the profiling of each solution.

## Runtime of codes

### Bruteforce knapsack solution

**Parallel**
```{r brute par}
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500, parallel=FALSE))
```
**Non-parallel**
```{r brute non-par}
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500, parallel=FALSE))
```

### Dynamic knapsack solution

```{r dynamic}
system.time(knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500))
```

### Greedy knapsack solution
```{r greedy}
system.time(greedy_knapsack(x = knapsack_objects[1:1000000,], W = 3500))
```
## Profiling
```{r profile setup, include=FALSE}
devtools::install_github("hadley/lineprof")
library(lineprof)
```

### Bruteforce knapsack solution

**Parallel**
```{r profile brute par}
lineprof(brute_force_knapsack(x = knapsack_objects[1:12,], W = 3500, parallel=TRUE))
```

Here we see that apart from allocation, all segments of the code are in similar timesteps - quite tricky to identify bottlenecks. However one could look over using some primitive functions instead of using lapply to find the row with near-optimal value. A suggestions might be using **max()**.

**Non-parallel**
```{r profile brute non-par}
lineprof(brute_force_knapsack(x = knapsack_objects[1:12,], W = 3500, parallel=FALSE))
```

Similar to the parallel solution this code has very little overhead that could be optimized.

### Dynamic knapsack solution
```{r profile dynamic}
lineprof(knapsack_dynamic(x = knapsack_objects[1:100,], W = 3500))
```

Here we identify that the segment in the code that takes most time to run is the replicate function. This could be handled by some other primitive, or maybe the pre-allocation can be circumvented by having dynamic size of the vector.

### Greedy knapsack solution
```{r profile greedy}
lineprof(greedy_knapsack(x = knapsack_objects[1:20000,], W = 3500))
```

Not alot to improve on here.

## Parallelizing brute force knapsack
The performance that could be gained is non-existent since the lapply used doesn't contain any calculations. So there is little to no sequential computations that are done. If we had a computationally heavy lapply segment then we could gain an decrease in computation time. 
